---
title: "NormalityTest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NormalityTest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r packages, include = FALSE}
library(NormalityTest)
```



# Introduction 

This vignette demonstrates the use of the package `NormalityTest`. The package comes with only one function `normality.df` that performs the Shapiro Wilk test for all the numerical variables of a given data frame. Each test can be accompanied by a graphical presentation  (density and qqplot) giving a piece of visual information.

In the next section, some examples demonstrating the various ways data can be tested and visualized using  `NormalityTest`.

# Exmples

In this section, we will use the famous iris data that, for ease of use, comes loaded with the package.

```{r}
head(iris)
```


## Exemple 1

```{r}
normality.df(iris)
```


## Exemple 2

```{r, fig.width=7, fig.height=5}
normality.df(iris, output = "figure")
```

## Exemple 3

```{r, fig.width=8}
Res<-normality.df(iris, output = "message")
Res$pvalues["PetWid"]
```
